---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HVP (Horizonatal Vertical Pleiotropy) 

<!-- badges: start -->
<!-- badges: end -->

**`HVP`** is an R package designed to disentangle horizontal and vertical pleiotropy leading to the correct estimation of genetic correlation between two traits. 

## Installation

You can install the development version of HVP from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lamessad/HVP")
```
## Steps for Mendelian Randomization Analysis with MRLOVA
**1. run conventional bivariate 'GREML' (e,g., in mtg2)  and extract input data from the information matrix generated. 
**2. run Mendelian randomization to estimate the causal effect size 

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(HVP)
data(example_data)
tau = example_data$tau
varb = example_data$varb
covg_hat = example_data$covg_hat
varg = example_data$varg
v_tau = example_data$v_tau
v_varb = example_data$v_varb
v_varg = example_data$v_varg
v_covg_hat = example_data$v_covg_hat
cov_varg_covg_hat = example_data$cov_varg_covg_hat
cov_varb_covg_hat = example_data$cov_varb_covg_hat
hvp(varg, varb,covg_hat,v_varg,v_varb,v_covg_hat,cov_varg_covg_hat,cov_varb_covg_hat,tau)

```

## Contact

Please contact Lamessa Amente (lamessa.amente@mymail.unisa.edu.au) or Hong Lee (hong.lee@unisa.edu.au) if you have any queries.
